RIScatter: Unifying BackCom, AmBC, SR and RIS From a Distribution Perspective

### 2022-11-01 main.tex
:lipstick: Update table style

\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bookmark}
\usepackage{booktabs}
\usepackage[american]{circuitikz}
\usepackage{cite}
\usepackage{fixmath}
\usepackage[acronym]{glossaries-extra}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage[short]{optidef}
\usepackage{pgfplots}
\usepackage{ragged2e}
\usepackage[subtle]{savetrees}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
\usepackage{tabularx}
\usepackage{tikz}
\usepackage{xcolor}
% dark mode
% \usepackage{xcolor} \pagecolor[rgb]{0,0,0} \color[rgb]{1,1,1}

@@

\title{RIScatter: Unifying Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface}

@@

	\begin{table*}[!t]
		\caption{Comparison of Scattering Applications}
		\label{tb:scattering_applications}
		\begin{tabularx}{\textwidth}{CCCCCCC}
			\toprule
			                              & \gls{mbc}                 & \gls{bbc}                 & \gls{ambc}                                      & \gls{sr}                                     & \gls{ris}                                  & RIScatter                                         \\ \midrule
			Coexisting systems            & 1                         & 1                         & 2 (competitive)                                 & 2 (collaborative)                            & 1                                          & 2 (collaborative)                                 \\ \midrule
			Scatterer contribution        & Backscatter modulation    & Backscatter modulation    & Backscatter modulation and primary interference & Backscatter modulation and primary multipath & Passive beamforming                        & Backscatter modulation and passive beamforming    \\ \midrule
			Cooperative transmissions     & ---                       & ---                       & No (individual transmitters)                    & Active beamforming                           & ---                                        & Active beamforming and smart reflection           \\ \midrule
			Cooperative reception         & ---                       & ---                       & No (separated receivers)                        & Joint detection or \gls{sic}                 & ---                                        & Backscatter detection as primary channel training \\ \midrule
			Primary detection             & ---                       & ---                       & Semi-coherent                                   & Coherent or semi-coherent                    & Coherent                                   & Coherent                                          \\ \midrule
			Backscatter detection         & Coherent                  & Coherent                  & Semi-coherent or noncoherent                    & Coherent                                     & ---                                        & Semi-coherent                                     \\ \midrule
			Reflection state distribution & Equiprobable (line-coded) & Equiprobable (line-coded) & Equiprobable (line-coded)                       & Equiprobable or Gaussian                     & Degenerate (\gls{csi}-adaptive)            & Flexible (\gls{csi}- and traffic-adaptive)        \\ \midrule
			Load-switching frequency      & Fast or slow              & Fast or slow              & Fast or slow                                    & Slow                                         & Slow (dynamic) or quasi-static (blockwise) & Fast or slow                                      \\ \bottomrule
		\end{tabularx}
	\end{table*}

@@

\begin{section}{Scattering Principles}
	\gls{rf} wave scattering and reflecting are usually realized by a \emph{variable-load antenna} or \emph{programmable metamaterial} and described by a unified signal model \cite{Liang2022}.
	A typical antenna-based scatterer consists of an integrated antenna, a load-switching modulator, an energy harvester, and on-chip components (e.g., microcontroller and sensors) \cite{Dobkin2012}.
	It first receives the impinging signals, then reradiates some back to the space and dissipates the remaining.
	In comparison, a typical metamaterial-based scatterer comprises an outer metamaterial layer of numerous sub-wavelength metallic/dielectric patches with tunable permittivity/permeability, a middle copper plate layer that reflects residual to avoid leakage, an inner circuit board layer that adjusts the amplitude and phase responses of patches, and an integrated microcontroller/\glsentryshort{fpga} that coordinates with the network and controls the circuit \cite{Wu2020}.
	Ideally, it reflects the incident waves at the air-metamaterial boundary without receiving them, and mainly applies a phase shift on the reflected wave.
	In practice, both kinds of scatterers have finite reflection states with non-zero reflection loss, and the scatter-absorb tradeoff depends on impedance matching.
	For a scatter node with $M$ reflection states, the reflection coefficient at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is
	\begin{equation}
		\Gamma_m = \frac{Z_m - Z^*}{Z_m + Z},
		\label{eq:reflection_coefficient}
	\end{equation}
	where $Z_m$ is the antenna load (resp. metamaterial unit) impedance at state $m$ and $Z$ is the antenna input (resp. medium characteristic) impedance.
	Backscatter modulation and passive beamforming are realized by manipulating the reflection coefficient.
	Specifically, \gls{bc}, \gls{ambc} and \gls{sr} employ scatter nodes as information sources that encode message by \emph{probabilistically switching} between different states.
	For $M$-ary \gls{qam}, constellation point $c_m$ maps to reflection coefficient $\Gamma_m$ by \cite{Thomas2012a}
	\begin{equation}
		\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
		\label{eq:backscatter_modulation}
	\end{equation}
	where $\alpha \in \mathbb{I}$ is the amplitude scattering ratio at the direction of interest.
	In contrast, \gls{ris} employ reflecting elements as channel reconfigurators that enable constructive/destructive signal superposition by \emph{deterministically choosing} the reflection pattern.
	For a \gls{ris} element with $M$ available states, phase shift $\theta_m$ maps to reflection coefficient $\Gamma_m$ by \cite{Wu2018}
	\begin{equation}
		\Gamma_m = \beta_m \exp(j \theta_m),
		\label{eq:passive_beamforming}
	\end{equation}
	where $\beta_m \in \mathbb{I}$ is the amplitude scattering ratio of state $m$.\footnote{Most existing \gls{ris} literatures assume lossless reflection $\beta_m=1$, $\forall m$.}
\end{section}

@@

		Based on the setup in Fig. \ref{fg:riscatter_network}, we compare the achievable rates of RIScatter and different scattering applications:

@@

			\item \emph{\gls{bbc}:}
			The primary symbol becomes deterministic $s[n]=1$ and the receive signal at each primary block is

@@

		Fig. \ref{fg:region_comparison} compares typical achieve rate points of different scattering applications.
		First, we observe both \gls{bbc} and \gls{sr} almost achieve noise-free backscatter transmission when $N$ is sufficiently large.
		For \gls{bbc} using coherent energy detection, the conditional \gls{pdf} of accumulated receive energy \eqref{eq:energy_distribution_bbc} is more skewed at a large $N$, such that the equivalent \gls{dmtmac} \eqref{eq:dmtmac} becomes more reliable.
		For \gls{sr} with \gls{sic} and \gls{mrc}, the effective backscatter \gls{snr} is increased by $N$ times and the penalty term $\epsilon$ becomes insignificant.
		However, such an \gls{sr} requires $N$ \gls{sic} processes to detect one backscatter symbol (tuple), and the semi-coherent primary rate benefit only appears at a very large $N$.
		When $N$ is moderate, the randomly scattered signals should be modelled as primary interference rather than quasi-static multipath components, and the \gls{sr} point will move towards the \gls{ambc} point.
		% \footnote{\gls{sr} is essentially a multiplicative \gls{noma} that cancels interference, while \gls{ambc} is essentially a multiplicative \gls{sdma} that treats interference as noise.}
		% Besides, the deterministic reflection pattern of \gls{ris} provides constructive primary signal superposition
		% \gls{ris} achieves the highest primary achievable rate using deterministic reflection pattern.
		In comparison, RIScatter performs semi-coherent backscatter detection and coherent primary detection to enable backscatter modulation and passive beamforming for arbitrary $N$, and the primary-backscatter tradeoff can be controlled by \gls{csi}- and weight-adaptive input distribution design.

>>>>

\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bookmark}
\usepackage{booktabs}
\usepackage[american]{circuitikz}
\usepackage{cite}
\usepackage{fixmath}
\usepackage[acronym]{glossaries-extra}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage[short]{optidef}
\usepackage{pgfplots}
\usepackage{ragged2e}
\usepackage[subtle]{savetrees}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
\usepackage{tabularx}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage{colortbl}
% dark mode
% \usepackage{xcolor} \pagecolor[rgb]{0,0,0} \color[rgb]{1,1,1}

@@

% \title{RIScatter: Unifying Scattering Techniques From a Distribution Perspective}
\title{RIScatter: Unifying BackCom, AmBC, SR and RIS From a Distribution Perspective}
% \title{RIScatter: Unifying Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface}

@@

	\begin{table*}[!t]
		\caption{Comparison of Scattering Applications}
		\label{tb:scattering_applications}
		\renewcommand{\arraystretch}{1.25}
		\begin{tabularx}{\textwidth}{CCCCCCC}
			\toprule
			% \rowcolor{gray!25}
			                              & \gls{mbc}                 & \gls{bbc}                 & \gls{ambc}                                      & \gls{sr}                                     & \gls{ris}                                  & RIScatter                                         \\ \midrule
			Coexisting systems            & 1                         & 1                         & 2 (competitive)                                 & 2 (collaborative)                            & 1                                          & 2 (collaborative)                                 \\
			\rowcolor{gray!25}
			Scatterer contribution        & Backscatter modulation    & Backscatter modulation    & Backscatter modulation and primary interference & Backscatter modulation and primary multipath & Passive beamforming                        & Backscatter modulation and passive beamforming    \\
			Cooperative transmissions     & ---                       & ---                       & No (individual transmitters)                    & Active beamforming                           & ---                                        & Active beamforming and smart reflection           \\
			\rowcolor{gray!25}
			Cooperative reception         & ---                       & ---                       & No (separated receivers)                        & Joint detection or \gls{sic}                 & ---                                        & Backscatter detection as primary channel training \\
			Primary detection             & ---                       & ---                       & Semi-coherent                                   & Coherent or semi-coherent                    & Coherent                                   & Coherent                                          \\
			\rowcolor{gray!25}
			Backscatter detection         & Coherent                  & Coherent                  & Semi-coherent or noncoherent                    & Coherent                                     & ---                                        & Semi-coherent                                     \\
			Reflection state distribution & Equiprobable (line-coded) & Equiprobable (line-coded) & Equiprobable (line-coded)                       & Equiprobable or Gaussian                     & Degenerate (\gls{csi}-adaptive)            & Flexible (\gls{csi}- and traffic-adaptive)        \\
			\rowcolor{gray!25}
			Load-switching frequency      & Fast or slow              & Fast or slow              & Fast or slow                                    & Slow                                         & Slow (dynamic) or quasi-static (blockwise) & Fast or slow                                      \\ \bottomrule
		\end{tabularx}
	\end{table*}

@@

\begin{section}{Scattering Principles}
	\gls{rf} wave scattering and reflecting are usually realized by a \emph{variable-load antenna} or \emph{programmable metamaterial} and described by a unified signal model \cite{Liang2022}.
	A typical antenna-based scatterer consists of an integrated antenna, a load-switching modulator, an energy harvester, and on-chip components (e.g., microcontroller and sensors) \cite{Dobkin2012}.
	It first receives the impinging signals, then reradiates some back to the space and dissipates the remaining.
	In comparison, a typical metamaterial-based scatterer comprises an outer metamaterial layer of numerous sub-wavelength metallic/dielectric patches with tunable permittivity/permeability, a middle copper plate layer that reflects residual to avoid leakage, an inner circuit board layer that adjusts the amplitude and phase responses of patches, and an integrated microcontroller/\glsentryshort{fpga} that coordinates with the network and controls the circuit \cite{Wu2020}.
	Ideally, it reflects the incident waves at the air-metamaterial boundary without receiving them, and mainly applies a phase shift on the reflected wave.
	In practice, both types of scatterers have finite reflection states with non-zero reflection loss, and the scattered signal can be decomposed into the \emph{structural} and \emph{antenna} mode components \cite{Hansen1989}.
	The former consistently contributes to environment multipath and can be modelled within \gls{csi}, while the latter depends on impedance mismatch and can be used for backscatter modulation and/or passive beamforming.
	For a scatter node with $M$ reflection states, the reflection coefficient at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is
	\begin{equation}
		\Gamma_m = \frac{Z_m - Z^*}{Z_m + Z},
		\label{eq:reflection_coefficient}
	\end{equation}
	where $Z_m$ is the antenna load (resp. metamaterial unit) impedance at state $m$ and $Z$ is the antenna input (resp. medium characteristic) impedance.
	% Backscatter modulation and passive beamforming are realized by manipulating the reflection coefficient.
	\gls{bc}, \gls{ambc} and \gls{sr} employ scatter nodes as information sources that encode message by \emph{probabilistically switching} between different states.
	For $M$-ary \gls{qam}, constellation point $c_m$ maps to reflection coefficient $\Gamma_m$ by \cite{Thomas2012a}
	\begin{equation}
		\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
		\label{eq:backscatter_modulation}
	\end{equation}
	where $\alpha \in \mathbb{I}$ is the amplitude scattering ratio at the direction of interest.
	In contrast, \gls{ris} employ reflecting elements as channel reconfigurators that enable constructive/destructive signal superposition by \emph{deterministically choosing} the reflection pattern.
	For a \gls{ris} element with $M$ available states, phase shift $\theta_m$ maps to reflection coefficient $\Gamma_m$ by \cite{Wu2018}
	\begin{equation}
		\Gamma_m = \beta_m \exp(j \theta_m),
		\label{eq:passive_beamforming}
	\end{equation}
	where $\beta_m \in \mathbb{I}$ is the amplitude scattering ratio of state $m$.\footnote{Most existing \gls{ris} literatures assume lossless reflection $\beta_m=1$, $\forall m$.}
\end{section}

@@

		Based on the setup in Fig. \ref{fg:riscatter_network}, we compare the achievable rates of RIScatter for different applications:

@@

			\item \emph{Legacy:} Conventional active transmission without antenna mode scattering, $\alpha=0$.
			\item \emph{\gls{bbc}:} The primary symbol becomes deterministic $s[n]=1$ and the receive signal at each primary block is

@@

		The simulation results are shown in Fig. \ref{fg:region_comparison}.
		First, we observe both \gls{bbc} and \gls{sr} almost achieve noise-free backscatter transmission when $N$ is sufficiently large.
		For \gls{bbc} using coherent energy detection, the conditional \gls{pdf} of accumulated receive energy \eqref{eq:energy_distribution_bbc} is more skewed at a large $N$, such that the equivalent \gls{dmtmac} \eqref{eq:dmtmac} becomes more reliable.
		For \gls{sr} with \gls{sic} and \gls{mrc}, the effective backscatter \gls{snr} is increased by $N$ times and the penalty term $\epsilon$ becomes insignificant.
		However, such an \gls{sr} requires $N$ \gls{sic} processes to detect one backscatter symbol (tuple), and the semi-coherent primary rate benefit only appears at a very large $N$.
		When $N$ is moderate, the randomly scattered signals should be modelled as primary interference rather than quasi-static multipath components, and the \gls{sr} point will move towards the \gls{ambc} point.
		% \footnote{\gls{sr} is essentially a multiplicative \gls{noma} that cancels interference, while \gls{ambc} is essentially a multiplicative \gls{sdma} that treats interference as noise.}
		% Besides, the deterministic reflection pattern of \gls{ris} provides constructive primary signal superposition
		% \gls{ris} achieves the highest primary achievable rate using deterministic reflection pattern.
		% Second, the passive beamforming gain by a single \gls{ris} node
		% Second, the average primary achievable rate decreases in the presence of a \gls{ambc} node and subtly/notably increases in the presence of a \gls{sr}/\gls{ris} node.
		Second, the average primary rate slightly increases/decreases in the presence of a \gls{ambc}/\gls{ris} node, while the multipath benefit of \gls{sr} is indistinguishable for a small $K$.
		This is because the cascaded channel strength can be orders of magnitude lower than the direct channel strength due to the double fading effect.
		\gls{ris} always ensures constructive superposition of direct and scattered signal components, while \gls{sr} only creates a rich-scattering environment that stochastically enhances the average primary rate.

		Third, RIScatter enables flexible
		% adapt the reflection state distribution of passive scatter devices based on \gls{csi} and link weights, in order to flexibly transition between backscatter modulation and passive beamforming.

		% the inter \gls{ambc} node decreases

		In comparison, RIScatter performs semi-coherent backscatter detection and coherent primary detection to enable backscatter modulation and passive beamforming for arbitrary $N$, and the primary-backscatter tradeoff can be controlled by \gls{csi}- and weight-adaptive input distribution design.
